%\documentclass[twocolumn]{article}
\documentclass{article}

%\usepackage{fullpage}

\title{About Me in \LaTeX}

\author{
  Riadiani Marcelita \\
  San Jos\'{e} State University \\
  riadiani.marcelita@sjsu.edu
  }

\begin{document}
\maketitle

\begin{abstract}
This is an introductory paper of how I came into being in this world. Whatever anyone else tells you about me, do not believe them. This is the truth and the only truth there ever will be.
\end{abstract}

\section{Personal History}\label{sec:personal}
I am a Computer Science student at SJSU by day, but a professional witch by night. During the day I trudge in the mortal world, eternally filled with boredom, and go through the motions of attending classes, finishing programming assignments, and applying for menial, mortal jobs.

The real fun begins after midnight, after I have submitted all of my assignments, projects, and papers due 11:59PM. After Riadiani the CS student retires, Riadiani the Witch emerges out of hiding. She will dust off her cauldron from the bottom of her bed and start a fire with a twist of her fingers. She will crack open the potions book and read enchantments all night long. Then, shortly before she has to wake up for her damned 7:30AM class, she will take her magical broom for a spin around the night sky.

\section{Academic/Career Goals}
If you ask me as a mortal, my career goals would be to find a great CS-related job in the work field after I graduate, get a decent salary, and afford a nice lifestyle. All those boring, responsible stuff.

Career goals in the witch world, though, is more vastly unbounded and unlimited than the mortal ones. Some of my witchly academic/career goals include:

\begin{itemize}
  \item {Being the world's most renowned potions master}
  \item {Achieve an Excellent or Better in the Annual Magical Enchantment Examinations}
  \item {Graduate summa cum laude from the Witches' Academy of Spells, Potions, and Enchantments}
  \item {Publish an article regarding chants, spells, and potion-making, such as one by Sheila Douglas' ~\cite{douglas}}
\end{itemize}

\section{Hobbies/Outside Interests}
As was mentioned in section~\ref{sec:personal}, I do love working on my potions-making and enchantment skills at night. I love reading outside of school, and one of my favorite books is Blake's Everyday Witch A to Z ~\cite{blake}, because it's just such a wonderful and funny book!

I would say my hobbies and outside interests do not stray afar from my every night witchly rituals. I do enjoy what I do very much. I am a witch through and through, and my life is a continuation proof of that!

\bibliographystyle{plainurl}
%\bibliographystyle{alpha}
\bibliography{biblio}

\end{document}